\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Thomas Liu} \\ \vspace{1pt}
    \small 437-232-2668 $|$ \href{t33liu@uwaterloo.ca}{\underline{t33liu@uwaterloo.ca}} $|$ 
    \faLinkedinSquare \href{https://www.linkedin.com/in/thomas-tian-yu-liu-a93206236/}{\underline{LinkedIn}} $|$
    \faGithub \href{https://github.com/Aliothie}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, Ontario}
      {Bachelor of Mathematics - Major in Statistics and Computational Mathematics}{Sep. 2022 -- Present}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, HTML/CSS, JavaScript: TypeScript, SQL, PowerBI, R, C$\#$, MATLAB, Racket} \\
     \textbf{Frameworks}{: Node.js, React.js, Express.js, Bootstrap, JSON, SCSS, React Native, JQuery, ASP.NET} \\
     \textbf{Developer Tools}{: Visual Studio, Git, Excel, Bash, LaTeX, XCode, Linux, Heroku, Netlify, Postman, Insomia} \\
     \textbf{Database}{: MongoDB, MySQL}\\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full Stack Developer}{Sep. 2023 - Dec. 2023}
      {\href{https://www.sparklease.com/en/Home/Index}{SparkLease Inc.}}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Used various tools such as \textbf{XML, CSS, JS} within \textbf{React Native} to develop \textbf{WeChat Mini APP} with engaging layout, robost filter system, and proficient account management functionality}
        \resumeItem{Utilized \textbf{ASP.NET} alongside \textbf{CSHTML, CSS, JS} to implement both \textbf{PC and Mobile Website} with engaging layout, comprehensive filter system, and efficient account management for the company}
        \resumeItem{Designed and implemented robust \textbf{APIs} using \textbf{MVC} architecture to ensure efficient data handling and streamlined user experiences}
        \resumeItem{Worked closely with database using \textbf{SQL} and \textbf{Microsoft AZURE} and comimg up with algorithm that provides recommendations to users using \textbf{C$\#$}}
      \resumeItemListEnd

    \resumeSubheading
      {IBM Enterprise Mentorship Program with a focus on Business Analysis}{Jul. 2022 - Aug. 2022}
      {IBM and Asian Business and Management Program}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Used \textbf{IBM Cognos Analytics} to analyze Toronto hospitals' medical supplies}
        \resumeItem{Analyzed data and made future projection based on the current supplies}
        \resumeItem{Provided suggestion about the distribution of medical supplies over the entire Toronto region}
    \resumeItemListEnd

    \resumeSubheading
      {Vex Robotics}{Jul. 2019 - Aug. 2020}
      {\href{https://trsnexus.com/home-1}{Team 905Y}}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Worked in a team of 4 to compete in \textbf{VEX \underline{\href{https://vrc-kb.recf.org/hc/en-us/articles/9660927408407-VRC-History-2019-2020-Tower-Takeover}{Tower Takeover Challenge}}}}
        \resumeItem{Engineered a competitive \textbf{robot} with advanced functionalities and precisioin}
        \resumeItem{Leveraged \textbf{C++} to enable robot to perform excellent functionality and automated tasks}
        \resumeItem{Ranked \textbf{13th} internationally for skill related challenge and world finalist}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://github.com/Aliothie/Side-Projects/tree/main/Snake}{\underline{\textbf{Snake Game}}} $|$ \emph{Python, Pygame}}{Dec. 2022 - Jan. 2023}
      \resumeItemListStart
        \resumeItem{Built a \textbf{Snake Game} using \textbf{Python} built-in functions and \textbf{Pygame}}
        \resumeItem{Improved \textbf{UI} and \textbf{UX} by customizing pictures and sound effects}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/Aliothie/Side-Projects/tree/main/Condo-Database}{\underline{\textbf{Condo Database Management}}} $|$ \emph{C++}}{Jan. 2022 - Jun. 2022}
      \resumeItemListStart
        \resumeItem{Developed a database that can access and modify all the data that has been stored into the program}
        \resumeItem{Used self-defined exception class to catch all the error message generated during the program}
        \resumeItem{Utilized polymorphism and class to increase security to the data stored}
      \resumeItemListEnd
    \resumeProjectHeading
      {\href{https://github.com/Aliothie/Side-Projects/tree/main/Flight-Membership}{\underline{\textbf{Flight Booking System}}} $|$ \emph{C++}}{Jan. 2022 - Jun. 2022}
      \resumeItemListStart
        \resumeItem{Developed using \textbf{C++ OOP} principles: recursion, pointer algorithm, inheritance, exception handling}
        \resumeItem{Implemented the system logic with the use of STL container and STL algorithms}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------Certificate-----------
\section{Certificate}
  \resumeItemListStart
    \resumeItem{CPA: Programming Essentials in C++}
    \resumeItem{CCNAv7: Switching, Routing, and Wireless Essentials}
    \resumeItem{CCNAv7: Introduction to Networks}
    \resumeItem{IBM Enterprise Mentorship Program with a focus on Business Analysis Certificate}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
